Declarative Data Analytic

### 2015-07-15 paper.tex
Openstack case study

\paragraph{6/9}

@@

\paragraph{6/24}

@@

\paragraph{7/1}

@@

  \item 
  \end{itemize}

@@

>>>>

\subsection{6/9}
\label{sec:meeting:69}

@@

\subsection{6/24}
\label{sec:meeting:624}

@@

\subsection{7/1}
\label{sec:meeting:624}

@@

@@

\paragraph{Future work}
Complete a root cause analysis case study on OpenStack.

\subsection{7/8}
\label{sec:meeting:678}

\paragraph{Thought}
I wonder if component-level dependency can also be specified in \saf{}. Because no
matter what dependency level we focus on, we still need to determine the
low-level logs by specifying the conditions over their fields. The higher level the
specification is, the more wildcard we are inserting into the specification.

For example, if we would like to specify a component-level dependency: $vm_1
\rightarrow vm_2$, we need to make it clear what logs are instances of $vm_1$
and $vm_2$. To do this, a candidate specification would be ``machine\_name =
$vm_1$. This specification is still in the scope of \saf{}. Based on this, the
specification over the logs is similar to specification over the directory paths
in the file system.

\paragraph{Todo}

\begin{itemize}
\item Finish the manual root cause analysis case study.
\item Meanwhile, clarify the work flow of the user.
\item Find as much automation as possible in the work flow. For example,
  automatic model generation.
\end{itemize}

\section{Root cause analysis case studies}
Manual root cause analysis case studies.

\begin{itemize}
\item Backtracking the execution according to causality relationship
  \begin{itemize}
  \item Identify the normal execution logs to explore: osloganal/data/logs/new\_testbed24/novadelete/delete-0.log
  \item Convert the log in JSON into an SQLite3 database. (done)
  \item Obtain domain-specific knowledge about OpenStack and the execution:
    data/models(Filtered Message Sequence)
  \item Specify the domain-specific knowledge in SAF --- on different levels ---
    and found corresponding traces.
    \begin{itemize}
    \item Level 1: event dependency
    \item Level 2: component dependency
    \end{itemize}
  \item Build the causality graph for different levels.
  \end{itemize}
\item Root cause detection of failure symptoms based on the backtracking technique
\end{itemize}
